Pretty darn good control: when are approximate solutions better than approximate models

### 2023-07-05 manuscript/manuscript.Rmd
minitypos

In this paper, we focus on a well-developed application of model-based management of the natural world that has long illustrated the trade-offs between model complexity and policy complexity: the management of marine fisheries.
Fisheries management is both an important issue to society and a rich & frequent test-bed of ecological management more generally.
Fisheries are an essential natural resource that provide the primary source of protein for one in every four humans, and have faced widely documented declines due to over-fishing [@Worm2006, @Costello2016].
Fisheries management centers around the process of sampling populations to determine fishing quotas based on population estimates.
This decision is often guided by a model of the dynamics of the system.
Our paper focuses on the decision side of this problem rather than the measurement step.

@@

## Discussion

@@

We compare deep reinforcement learning-based policies against classical management strategies (optimal CMort and optimal CEsc policies policies). 
While the latter are inspired by the shape of optimal solutions in the single-species setting, they are optimized in a model-free way as well: e.g. the optimal mortality rate is computed empirically from simulated data.

>>>>

In this paper, we focus on a well-developed application of model-based management of the natural world that has long illustrated the trade-offs between model complexity and policy complexity: the management of marine fisheries.
Fisheries management is both an important issue to society as well as a rich and frequent test-bed of ecological management more generally.
Fisheries are an essential natural resource that provide the primary source of protein for one in every four humans, and have faced widely documented declines due to over-fishing [@Worm2006, @Costello2016].
Fisheries management centers around the process of sampling populations to determine fishing quotas based on population estimates.
This decision is often guided by a model of the dynamics of the system.
Our paper focuses on the decision side of this problem rather than the measurement step.

@@

@@

We compare deep reinforcement learning-based policies against classical management strategies (CMort and CEsc). 
While the latter are inspired by the shape of optimal solutions in the single-species setting, they are optimized in a model-free way as well: e.g. the optimal mortality rate is computed empirically from simulated data.
